---
output:
  rmdformats::readthedown:
    self_contained: false
    includes:
      in_header: GA_Script.html
params:
  institution_name: "nothing"
  institution_long_name: "nothing"
  institution_id: "nothing"
  comparison_table: "nothing"
  spark_width: 200
  spark_height: 60
  weatherspark: "nothing"
title: "`r paste0(params$institution_name)`"

---

```{css, echo=FALSE}
img {
  max-width: 100%;
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(dev="png", echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
source("_packages.R")
source("R/functions.R")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
#`UNITID Unique identification number of the institution`

try({

	focal_conference <- FirstNaOmit((subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution`==params$institution_id))$`NCAA NAIA conference number cross country track`)

	focal_classification <- FirstNaOmit((subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution`==params$institution_id))$`Carnegie Classification 2021 Basic`)

	conference_UNITID <- unique(subset(comparison_table, comparison_table$`NCAA NAIA conference number cross country track`==focal_conference)$`UNITID Unique identification number of the institution`)
	conference_UNITID <- conference_UNITID[conference_UNITID!=params$institution_id]

	classification_UNITID <- unique(subset(comparison_table, comparison_table$`Carnegie Classification 2021 Basic`==focal_classification)$`UNITID Unique identification number of the institution`)
	classification_UNITID <- classification_UNITID[classification_UNITID!=params$institution_id]

	focal_conference <- subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution` %in% conference_UNITID)
	focal_conference_name <- subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution` %in% conference_UNITID)$`NCAA NAIA conference number cross country track`[1]

	focal_conference$Comparison = "Conference"

	focal_classification <- subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution` %in% classification_UNITID)
	focal_classification_name <- subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution` %in% classification_UNITID)$`Carnegie Classification 2021 Basic`[1]
	focal_classification$Comparison = "Classification"

	focal_focal <- subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution`==params$institution_id)
	focal_focal$Comparison = "Focal"

	focal_table <- dplyr::bind_rows(focal_focal, focal_conference, focal_classification)
	focal_table$`IPEDS Year` <- as.numeric(focal_table$`IPEDS Year`)
	focal_table <- focal_table[order(focal_table$`IPEDS Year`, decreasing=TRUE),]

	most_current_info <- apply(focal_focal, 2, FirstNaOmit)

	harvard_price <- FirstNaOmit(subset(comparison_table, comparison_table$`UNITID Unique identification number of the institution`=="166027")$`Average net price students awarded grant or scholarship aid`)
	RatioToHarvard <- as.numeric(most_current_info['Average net price students awarded grant or scholarship aid'])/as.numeric(harvard_price)
}, silent=TRUE)

try({
	notes <- c()


	if(most_current_info['Institution is active in current year'] != "Yes") {
		notes <- append(notes, paste0("Institution is not active", ifelse(grepl('-', most_current_info['Date institution closed']), "", paste0("; it closed on ", most_current_info['Date institution closed']))))
	}
}, silent=TRUE)

try({
	if(most_current_info['OPE Title IV eligibility indicator code'] %in% c("Deferment only - limited participation", "Not currently participating in Title IV, does not have OPE ID number", "Not currently participating in Title IV, has an OPE ID number", "Stopped participating during the survey year")) {
		notes <- append(notes, "This institution has limited or no participation in the federal Title IV program. This prevents students from receiving some types of federal aid. Some institutions are ineligible for various reasons. Others could be eligible but choose not to receive federal funds in order to avoid following the requirements that go along with them, such as <a href='https://www.theatlantic.com/education/archive/2016/07/the-controversial-reason-some-religious-colleges-forgo-federal-funding/490253/'>guidelines on how to respond to sexual assault or bans on some kinds of discrimination</a>.")
	}
}, silent=TRUE)
```

```{r}
try({
	if(most_current_info['California Travel Ban'] == "TRUE") {
		notes <- append(notes, "California considers the state this institution is in to have one or more anti-LGBTQ+ laws. It prohibits California-sponsored travel to this state as a safety measure. See more <a href='https://oag.ca.gov/ab1887'>here</a>.")
	}
}, silent=TRUE)
```

```{r}
try({
	if(most_current_info['State'] == "Texas") {
		notes <- append(notes, "The state attorney general has <a href='https://www.washingtonpost.com/nation/2022/12/14/texas-transgender-data-paxton/'>sought to identify transgender individuals from state drivers license data</a>. Family and protective services have been ordered to <a href='https://www.washingtonpost.com/nation/2022/02/23/greg-abbott-gender-affirming-care-child-abuse-directive/'>investigate all parents of transgender children for abuse, as well</a>.")
	}
}, silent=TRUE)
```


```{r}
try({
	if(most_current_info['AAUP_Censure'] == "Yes") {
		notes <- append(notes, "Unsatisfactory conditions of academic freedom and tenure have been found to prevail at this institution according to the <a href='https://www.aaup.org/our-programs/academic-freedom/censure-list'>AAUP</a>")
	}
}, silent=TRUE)
```

```{r}
try({
	if(as.numeric(most_current_info['Full time undergrad enrollment divided by tenure stream faculty'])>200) {
		notes <- append(notes, "There are extremely few tenure-track faculty relative to the number of students.For something like an art or music school where instruction is done nearly entirely by rotating artists or musicians, this may be fine; for other schools, it can indicate a <a href='https://www.aaup.org/issues/tenure'>risk to academic freedom</a> and thus educational quality, as faculty members *may* be able to lose their positions because of their speech, publications, or research findings.")
	}
}, silent=TRUE)
```

```{r}
chief_admins <- humaniformat::last_name(focal_focal$`Name of chief administrator`)[1:6]

try({
	if(length(chief_admins)/length(unique(chief_admins))<4 && length(chief_admins)>3 && length(unique(chief_admins))>3) {
		admin_vector <- c()
		for (admin in unique(chief_admins)) {
			years <- focal_focal$`IPEDS Year`[which(chief_admins==admin)]
			admin_vector <- append(admin_vector, paste0(admin, " (", paste0(years, collapse=", "), ")"))
		}
		notes <- append(notes, paste0("Over the most recent ", length(chief_admins), " years for which data are available, there have been ", length(unique(chief_admins)), " different chief administrators (", gsub(",,", ",", paste(unique(admin_vector), collapse=", ")) ,") suggesting somewhat rapid turnover"))
	}
}, silent=TRUE)
```

```{r}
try({
	if(as.numeric(most_current_info['Revenue minus expenses'])<0) {
		notes <- append(notes, paste0("In the most recent year available, this institution ran a deficit of $", formatMe(abs(as.numeric(most_current_info['Revenue minus expenses'])))))
	}
}, silent=TRUE)
```

```{r}
degrees <- c("Certificate of less than 1 year", "Certificate of less than 12 weeks", "Certificate of at least 12 weeks but less than 1 year", "Certifiicate of at least 1 year but less than 2 years", "Associate s degree", "Certificate of at least 2 years but less than 4 years", "Bachelor s degree", "Postbaccalaureate certificate", "Master s degree", "Post master s certificate", "Other degree", "Doctor s degree  research scholarship", "Doctor s degree  professional practice", "Doctor s degree  other")
most_current_degrees <- most_current_info[degrees]
most_current_degrees <- which(most_current_degrees=="Yes")
degrees_cleaned <- gsub("  ", ": ", gsub(" s ", "'s ", gsub("Certifiicate", "Certificate", degrees)))
most_current_info['Degrees offered'] <- paste(degrees_cleaned[most_current_degrees], collapse=", ")
```

```{r}
```

```{r}
try({
	focal_focal_ug_ft_enrollment <- focal_focal %>% dplyr::select(c('Undergrad full time', 'IPEDS Year'))
	focal_focal_ug_ft_enrollment$UG_FT <- as.numeric(focal_focal_ug_ft_enrollment$`Undergrad full time`)
	focal_focal_ug_ft_enrollment <- focal_focal_ug_ft_enrollment[!is.na(focal_focal_ug_ft_enrollment$UG_FT),]
	focal_focal_ug_ft_enrollment$Year <- as.numeric(focal_focal_ug_ft_enrollment$`IPEDS Year`)
	enrollment_year_start_row <- which.min(focal_focal_ug_ft_enrollment$Year)
	enrollment_year_stop_row <- which.max(focal_focal_ug_ft_enrollment$Year)
	if(focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_stop_row]/focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_start_row] < 0.90) {
		notes <- append(notes, paste0("From ", min(focal_focal_ug_ft_enrollment$Year), " to ", max(focal_focal_ug_ft_enrollment$Year), ", full time undergraduate enrollment dropped from ", focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_start_row], " to ", focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_stop_row], ", a decline of ", 100-round(100*focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_stop_row]/focal_focal_ug_ft_enrollment$UG_FT[enrollment_year_start_row],1), "%"))
	}
}, silent=TRUE)
```

```{r}
db <- dbConnect(RSQLite::SQLite(), "data/db_IPEDS.sqlite")
majors <- tbl(db, 'Completions_with_percentage') %>% as.data.frame() %>% dplyr::filter(UNITID==params$institution_id) %>% dplyr::select(-UNITID) %>% dplyr::select(-Institution)
dbDisconnect(db)
```


```{r}
comparison_conversions <- read.csv("data/ConversionToSummaryCharts.csv")
comparison_vector <- c("Conference", "Classification")
headings <- unique(comparison_conversions$Category)
comparison_df <- data.frame(matrix("", nrow=nrow(comparison_conversions), ncol=4+length(comparison_vector)))
colnames(comparison_df) <- c(params$institution_name, "Change", "Trend", focal_conference_name, focal_classification_name, "Heading")
rownames(comparison_df) <- comparison_conversions$Rename
max_year_overall <- 0
min_year_overall <- Inf
for(row_index in sequence(nrow(comparison_conversions))) {
	try({
		focal_field <- comparison_conversions$ColumnName[row_index]
		values_for_range <- as.numeric(focal_table[,focal_field])
		values_for_range <- values_for_range[is.finite(values_for_range)]
		focal_field_range <- range(values_for_range, na.rm=TRUE)
		focal_table[,focal_field] <- as.numeric(focal_table[,focal_field])
		table_to_plot <- focal_table[,colnames(focal_table) %in% c('UNITID Unique identification number of the institution', 'IPEDS Year','Comparison', focal_field, "Institution entity name")]
		colnames(table_to_plot)[grepl("IPEDS Year", colnames(table_to_plot))] <- "Year"
		table_to_plot <- table_to_plot[!is.na(table_to_plot[,focal_field]),]
		table_to_plot <- table_to_plot[order(table_to_plot$Year, decreasing=TRUE),]
		max_year <- Inf
		min_year <- 0
		table_to_plot_focal_only <- subset(table_to_plot, table_to_plot$Comparison=="Focal")
		comparison_df$Heading[row_index] <- comparison_conversions$Category[row_index]
		max_year <- max(table_to_plot_focal_only$Year)
		min_year <- min(table_to_plot_focal_only$Year)
		max_year_overall <- max(max_year, max_year_overall)
		min_year_overall <- min(min_year, min_year_overall)
		table_to_plot <- subset(table_to_plot, Year<=max_year & Year>=min_year)
		
		
		
		# Plot the focal measure
		suppressWarnings(suppressMessages({ # ggplot needs to talk way less
		
				
			plotting_data <- table_to_plot_focal_only
			colnames(plotting_data)[which(colnames(plotting_data)==focal_field)] <- "Number"
			plotting_data <- subset(plotting_data, !is.na(plotting_data$Number))
			plotting_data$NumberText <- paste0(sapply(plotting_data$Number, formatMe, digits=0))
			oldest <- plotting_data %>% slice(which.max(Year))
			youngest <- plotting_data %>% slice(which.min(Year))
			p <- ggplot(plotting_data, aes(x=Year, y=Number)) + geom_link2(aes(colour = after_stat(ifelse(y >= 0, "black", "red")))) +
			scale_colour_manual(values=c("black", "red")) +
				theme(
				axis.title=element_blank(),
				panel.background = element_rect(fill='transparent'),
				plot.background = element_rect(fill='transparent', color=NA),
				axis.text.x = element_blank(), 
				axis.ticks = element_blank(),
				panel.grid.major = element_blank(),
				panel.grid.minor = element_blank(),
				legend.background = element_rect(fill='transparent'),
				legend.box.background = element_rect(fill='transparent'),
				legend.position="none"
			) +
			scale_y_continuous(breaks=c(youngest$Number), position="left", labels=c(youngest$NumberText), sec.axis = sec_axis(~ ., breaks = oldest$Number, labels=oldest$NumberText)) +
			theme(axis.text.y = element_text(colour = "black"))	
		}))
		
		filename_png <- paste0("images/", utils::URLencode(gsub(" ", "", params$institution_name)), "_", row_index, ".png")

		suppressWarnings(suppressMessages({
			ggsave(
			plot = p,
			filename = paste0('docs/', filename_png),
			bg = "transparent",
			width = params$spark_width*2.5,
			height= params$spark_height*2.5,
			units = "px"
			)
		}))

		#comparison_df$Change[row_index] <- paste0("<img src=", filename_png, " width=", spark_width, " height=", spark_height, ">")
		comparison_df$Change[row_index] <- paste0("<img src=", filename_png, " alt='Line plot from ", youngest$NumberText, " to ", oldest$NumberText, " from ", youngest$Year, " to ", oldest$Year, "' >")

		most_recent_value <- head(table_to_plot_focal_only[focal_field],1)
		original_most_recent_value <- most_recent_value
		if(comparison_conversions$Units[row_index]=="Dollars") {
			most_recent_value <- formatMe(most_recent_value, prefix="$")
		} else if(comparison_conversions$Units[row_index]=="Percent") {
			most_recent_value <- paste0(formatMe(most_recent_value), '%')
		} else {
			most_recent_value <- formatMe(most_recent_value)
		}
		# if(comparison_conversions$Heading=="Graduation") {
		# 	if(comparison_conversions$Better[row_index]=="Higher") {
		# 		most_recent_value <- paste0('<b><span style=\\"color:', GetColorFromPercentile(original_most_recent_value), ';\\">', most_recent_value, "</span></b>")
		# 	}
		# 	if(comparison_conversions$Better[row_index]=="Lower") {
		# 		most_recent_value <- paste0('<b><span style=\\"color:', GetColorFromPercentile(original_most_recent_value, direction=1), ';\\">', most_recent_value, "</span></b>")
		# 	}
		# }

		most_recent_value <- paste0(most_recent_value, " (", max_year, ")")
		comparison_df[row_index,1] <- most_recent_value
			
		linear_fit_data <- table_to_plot_focal_only
		colnames(linear_fit_data)[which(colnames(linear_fit_data)==focal_field)] <- "Dependent"
		try({
		fit <- stats::lm(Dependent ~ Year, data=linear_fit_data)
		if(summary(fit)$coefficients[2,4]<0.05) { # a significant trend; not correcting for multiple comparisons, just getting an heuristic on changes over time
			change_symbol <- '↑'
			if(sign(summary(fit)$coefficients[2,1])<0) {
				change_symbol <- '↓'
			}
			slope <- summary(fit)$coefficients[2,1] 
			if(comparison_conversions$Units[row_index]=="Dollars") {
				slope <- paste0(ifelse(sign(slope)<0, "-", ""), '$', formatMe(abs(slope),0))
			} else if (comparison_conversions$Units[row_index]=="Percent") {
				slope <- paste0(abs(formatMe(slope,2)), '%')
			} else {
				slope <- formatMe(slope,0)
			}

			comparison_df$`Trend`[row_index] <- paste0(change_symbol, "<br />",  slope, ' per year')
		}
		}, silent=TRUE)
		
		
		# now for the stars
		#star_symbol <- '⭐'
		star_symbol <- '✪'
		if(comparison_conversions$Better[row_index]!="None") {
			for (grouping_index in sequence(length(comparison_vector))) {
				table_to_plot_comparison_only <- subset(table_to_plot, table_to_plot$Comparison==comparison_vector[grouping_index])
				comparison_values <- table_to_plot_comparison_only[which(table_to_plot_comparison_only$Year==max_year), focal_field]
				quantile_score <- stats::ecdf(comparison_values)(original_most_recent_value)
				if(comparison_conversions$Better[row_index]=="Lower") {
					quantile_score <- 1-quantile_score
				}
				star_string <- paste0(rep(star_symbol, max(1, ceiling(10*quantile_score/2))), collapse="") # there's always at least one star
				comparison_df[row_index, grouping_index+3] <- paste0(star_string, "<br />Better (", tolower(comparison_conversions$Better[row_index]), ") than ", round(100*quantile_score), '%')
			}
		}
		
	}, silent=TRUE)
}

colnames(comparison_df) <- gsub("Change", paste0("Change over ≤\n", max_year_overall-min_year_overall, " years"), colnames(comparison_df))
colnames(comparison_df) <- gsub("Not applicable", "Schools not in an athletic conference", colnames(comparison_df))

comparison_df <- subset(comparison_df, nchar(comparison_df[,1])>0)

```




```{r, eval=TRUE}
try({
	# all categories based on how the US federal government bins people.
	ethnicities <- c("American Indian or Alaska Native", "Asian", "Black or African American", "Hispanic or Latino", "Native Hawaiian or Other Pacific Islander", "White", "Two or more races", "Race ethnicity unknown", "Nonresident alien")
	faculty_ranks <- c("Tenure-stream", "NTT-stream")
	genders <- c("women", "men") 

	faculty_ethnicity <- data.frame(matrix("", nrow=length(ethnicities), ncol=3))
	rownames(faculty_ethnicity) <- ethnicities
	colnames(faculty_ethnicity) <- c(params$institution_name, "Tenure track", "Non-tenure track")
	for (rank_index in sequence(length(faculty_ranks))) {
		for (category_index in sequence(length(ethnicities))) {
			try({
				category_name <- paste0(faculty_ranks[rank_index], " ", ethnicities[category_index])
				ethnicity_df <- focal_focal[,colnames(focal_focal) %in% c('IPEDS Year', category_name, paste0(faculty_ranks[rank_index], " Grand total"))] 
				ethnicity_df$Year <- as.numeric(ethnicity_df$`IPEDS Year`)
				ethnicity_df$Percentage <- 100*ethnicity_df[,category_name]/ethnicity_df[,paste0(faculty_ranks[rank_index], " Grand total")]
				ethnicity_df <- subset(ethnicity_df, !is.na(ethnicity_df$Percentage))
				ethnicity_df$PercentageText <- paste0(sapply(ethnicity_df$Percentage, formatMe, digits=1),'%')
				oldest <- ethnicity_df %>% slice(which.max(Year))
				youngest <- ethnicity_df %>% slice(which.min(Year))
				
				
				p <- ggplot(ethnicity_df, aes(x=Year, y=Percentage)) + geom_link2(aes(colour = after_stat(ifelse(y >= 0, "deepskyblue3", "red")))) +
					scale_colour_manual(values=c("deepskyblue3", "red")) +
					theme(
						axis.title=element_blank(),
						panel.background = element_rect(fill='transparent'),
						plot.background = element_rect(fill='transparent', color=NA),
						axis.text.x = element_blank(), 
						axis.ticks = element_blank(),
						panel.grid.major = element_blank(),
						panel.grid.minor = element_blank(),
						legend.background = element_rect(fill='transparent'),
						legend.box.background = element_rect(fill='transparent'),
						legend.position="none"
					) +
					coord_cartesian(ylim=c(0, NA)) + 
				scale_y_continuous(breaks=c(0,youngest$Percentage), position="left", labels=c("", youngest$PercentageText), sec.axis = sec_axis(~ ., breaks = oldest$Percentage, labels=oldest$PercentageText)) +
				theme(axis.text.y = element_text(colour = "black"))
				
				filename_png <- paste0("images/", utils::URLencode(gsub(" ", "", params$institution_name)), "_faculty_", category_index, "_", rank_index, ".png")
				
				suppressWarnings(suppressMessages({
					ggsave(
					plot = p,
					filename = paste0('docs/', filename_png),
					bg = "transparent",
					width = params$spark_width*2.5,
					height= params$spark_height*2.5,
					units = "px"
					)
				}, silent=TRUE))
				
				

				faculty_ethnicity[category_index, rank_index+1] <- paste0("<img src=", filename_png, " alt='Line plot from ", youngest$PercentageText, " to ", oldest$PercentageText, " from ", youngest$Year, " to ", oldest$Year, "' >")
			}, silent=TRUE)
		}
	}
}, silent=TRUE)


```
<a href='`r PrependHttpsIfNeeded(most_current_info['Institution s internet website address'])`'>`r most_current_info['Institution entity name']`</a> is located in `r most_current_info['City location of institution']`, `r most_current_info['State']`. It is a `r tolower(most_current_info['Sector of institution'])` institution.

```{r, results='asis'}
try({
	wikipedia_summary <- GetWikipediaSummaryFirstParagraph(most_current_info['Institution entity name'])
	if(!is.null(wikipedia_summary)) {
		cat("*From [Wikipedia](https://en.wikipedia.org/wiki/", utils::URLencode(most_current_info['Institution entity name']), ")*: ")
		cat(gsub("\\.\\.", '.', wikipedia_summary))
		cat("\n\n")
	}
}, silent=TRUE)
```

```{r, results='asis'}
if(length(notes)>0) {
	cat("# Notes\nThese are items that bear looking into more closely: some may be problems, some may be neutral, some may even be good. For example, a decline in enrollment is often problematic, but it may reflect a school specializing (i.e., focusing on just nursing rather than nursing and business).\n\n")
	for (note in notes) {
		cat(paste0('* ', note, "\n\n"))	
	}	
}
```

# Overview of institution

* **Institution kind**: `r most_current_info['Carnegie Classification 2021 Basic']`
* **Undergrad program**: `r most_current_info['Carnegie Classification 2021 Undergraduate Instructional Program']`
* **Graduate program**: `r most_current_info['Carnegie Classification 2021 Graduate Instructional Program']`
* **Enrollment profile**: `r most_current_info['Carnegie Classification 2021 Enrollment Profile']` (see more details below)
* **Average net price for undergrads on financial aid**: $ `r formatMe(as.numeric(most_current_info['Average net price students awarded grant or scholarship aid']))` (`r ifelse(RatioToHarvard>1, paste0(round(RatioToHarvard,1), " times the equivalent cost of Harvard)"), paste0("This is ", 100*round(RatioToHarvard,1), "% the cost of Harvard)"))`
* **Size and setting**: `r most_current_info['Carnegie Classification 2021 Size and Setting']`
`r ifelse(most_current_info['Tribal college']=="Yes", '* This is a **Tribal College**\n', "")`
`r ifelse(most_current_info['Historically Black College or University']=="Yes", '* This is a **Historically Black College or University (HBCU)**\n', "")`
`r ifelse(!is.na(most_current_info['Graduation Rate Bachelors in within 150 percent of normal time Grand total']), paste0('* **Graduation rate (within 6 years) for students seeking a Bachelors**: ', round(as.numeric(most_current_info['Graduation Rate Bachelors in within 150 percent of normal time Grand total']),1), '% (this is what is usually reported as "graduation rate")\n'), "")`
`r ifelse(!is.na(most_current_info['Graduation Rate Bachelors in 4 years or less Grand total']), paste0('* **Graduation rate (within 4 years) for students seeking a Bachelors**: ', round(as.numeric(most_current_info['Graduation Rate Bachelors in 4 years or less Grand total']),1), '%\n'), "")`
`r ifelse(!is.na(most_current_info['Graduation Rate Transfer out of bachelors Grand total']), paste0('* **Percent of students seeking a Bachelors who transfer out of this institution**: ', round(as.numeric(most_current_info['Graduation Rate Transfer out of bachelors Grand total']),1), '%\n'), "")`
* **Student to tenure-stream faculty ratio**: `r round(as.numeric(most_current_info['Full time undergrad enrollment divided by tenure stream faculty']),1)` (undergrads to tenure-stream faculty)
* **Student to faculty ratio**: `r round(as.numeric(most_current_info['Full time undergrad enrollment divided by total instructors']),1)` (undergrads to all faculty)
* **Degrees offered**: `r most_current_info['Degrees offered']`
* **Schedule**: `r most_current_info['Calendar system']`
* **Institution provides on campus housing**: `r most_current_info['Institution provide on campus housing']`
`r ifelse(is.finite(as.numeric(most_current_info['Total dormitory capacity'])), ifelse(as.numeric(most_current_info['Total dormitory capacity'])>0, paste0("* **Dorm capacity**: There are enough dorm beds for ", as.numeric(most_current_info['Total dormitory capacity']), " students"), ""), "")`
* **Freshmen required to live on campus**: `r most_current_info['Full time first time degree certificate seeking students required to live on campus']`
* **Meal plan**: `r most_current_info['Institution provides board or meal plan']`
* **Covid vaccination requirement for students**: `r ifelse(most_current_info['AllStudentsVaccinatedAgainstCovid19']=="Yes", "At some point during the pandemic (this may have changed), this institution required students to be vaccinated against covid", "This institution was never reported as requiring covid vaccination for students")` (based on info from [here](https://www.chronicle.com/blogs/live-coronavirus-updates/heres-a-list-of-colleges-that-will-require-students-to-be-vaccinated-against-covid-19))
* **Covid vaccination requirement for faculty/staff**: `r ifelse(most_current_info['AllEmployeesVaccinatedAgainstCovid19']=="Yes", "At some point during the pandemic (this may have changed), this institution required faculty and/or staff to be vaccinated against covid", "This institution was never reported as requiring covid vaccination for faculty and/or staff")` (based on info from [here](https://www.chronicle.com/blogs/live-coronavirus-updates/heres-a-list-of-colleges-that-will-require-students-to-be-vaccinated-against-covid-19))
* **Advanced placement (AP) credits used**: `r most_current_info['Advanced placement AP credits']`

`r ifelse(most_current_info['Percent indicator of undergraduates formally registered as students with disabilities']=="More than 3 percent", paste0("* **Disabilities**: ", most_current_info['Percent of undergraduates who are formally registered as students with disabilities when percentage is more than 3 percent'], " percent of undergrads are registered as having disabilities.\n"), paste0("* **Disabilities**: ", most_current_info['Percent indicator of undergraduates formally registered as students with disabilities'], " of undergrads are registered as having disabilities.\n"))`


# Overview of location

* **Abortion in this state**: `r most_current_info['Abortion']` (based on https://states.guttmacher.org/policies/)
* **Gun law stringency**: `r most_current_info['Gun Law Stringency']` (higher grade = [more stringent](https://worldpopulationreview.com/state-rankings/strictest-gun-laws-by-state))
* **State rep support for contraception**: `r round(100*as.numeric(most_current_info['Proportion of reps voting in favor of respect for right to contraception act']),1)`% of US reps from this state [voted in favor](https://www.congress.gov/bill/117th-congress/house-bill/8373) of legal protections for contraception.
* **State rep support for recognizing same-sex and interracial marriage**: `r round(100*as.numeric(most_current_info['Proportion of reps voting in favor of respect for marriage act']),1)`% of US reps from this state [voted in favor](https://www.congress.gov/bill/117th-congress/house-bill/8404) of requiring states to recognize same-sex and interracial marriages performed in other states
* **Ecological region**: `r most_current_info['eco_name']`
* **Biome**: `r most_current_info['biome']`
* **Climate**: See overview at [WeatherSpark.com](`r GetClosestWeatherspark(most_current_info, weatherspark)`).

## Map

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
leaflet() %>%
  addTiles() %>%  
  setView(lng = as.numeric(most_current_info['Longitude location of institution']), lat = as.numeric(most_current_info['Latitude location of institution']), zoom = 16) %>% 
  addMarkers(lng=as.numeric(most_current_info['Longitude location of institution']), lat=as.numeric(most_current_info['Latitude location of institution']), popup=as.numeric(most_current_info['Institution name']))
```

# Enrollment

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Enrollment"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)] # this gets rid of empty columns
		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)

```

# Student financing

At many universities, almost no students pay the listed tuition and fees ("sticker price"): instead, their financial aid package lowers this dramatically, but how much students pay can vary substantially based on family income and other factors. The tuition below is the average across many students receiving aid: your family may be asked to pay less or more than this. 

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Student financing"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]
		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)

```

# Teaching

```{r, eval=TRUE}
	try({
	pretty_table <- comparison_df[which(comparison_df$Heading == "Teaching"),]
	pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

	pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# Student details

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Student conditions"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]
		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)

```

# Institution finances

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Institution finances"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)

```

# Graduation rates

Graduation rates for bachelor's degrees within 150% of normal time (6 years for a 4-year degree). Note that this uses US federal demographic data: it only has two genders and a specified set of ethnicities and races. For groups with small numbers, the graduation rate may be highly variable year to year (do all three people in this group graduate this year or just two of three, for example).

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Graduation"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# Freshmen demographics

Demographic data for first time degree-seeking students. Note that this uses US federal demographic data: it only has two genders and a specified set of ethnicities and races.

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Freshmen"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# Tenure track faculty

Tenure track faculty are those who are eligible for tenure. This includes both pre-tenure and tenured faculty. Once faculty get tenure, they are (generally) protected from being fired for intellectual reasons, helping to ensure their freedom in teaching and research. They can still lose their positions for misconduct, financial problems, not fulfilling their duties, or other reasons. Note that this chart uses US federal demographic data: it only has two genders and a specified set of ethnicities and races.

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Tenure stream faculty"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```


# Non-tenure track faculty

Non-tenure track faculty are not eligible for tenure. Some are hired one semester at a time, some have multi-year contracts. They typically have a higher teaching load than tenure track faculty, leaving less time for research or other creative endeavors. They are also easier to fire than tenured faculty. Sometimes they are external experts (a noted musician, a former senator) who are hired to teach some classes without the expected permanence of a tenure-track position. Note that this chart uses US federal demographic data: it only has two genders and a specified set of ethnicities and races.

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "Non-tenure stream faculty"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```


# Library facilities

```{r, eval=TRUE}
	try({
	pretty_table <- comparison_df[which(comparison_df$Heading == "Library facilities"),]
	pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

	pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# SAT scores

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "SAT scores"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# ACT scores

```{r, eval=TRUE}
	try({
		pretty_table <- comparison_df[which(comparison_df$Heading == "ACT scores"),]
		pretty_table <- pretty_table[,which((apply(pretty_table, 2, as.character) %>% apply(2, nchar) %>% apply(2, max, na.rm=TRUE))>0)]

		pretty_table %>% dplyr::select(-c(Heading)) %>% knitr::kable(align="c") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
	}, silent=TRUE)
```

# Degrees by major 

```{r, eval=TRUE}
	try({
	majors$Field <- paste0('<a href="', paste0("majors_", utils::URLencode(gsub(" ", "", majors$Degree)), "_", EncodeField(majors$Field) ,".html"), '">', majors$Field, "</a>")
	}, silent=TRUE)
```

## Bachelors

```{r, eval=TRUE}
	DT::datatable(subset(majors, Degree=="Bachelors"), rownames=FALSE)
```

## Masters

```{r, eval=TRUE}
	DT::datatable(subset(majors, Degree=="Masters"), rownames=FALSE)
```

## Doctorate

```{r, eval=TRUE}
	DT::datatable(subset(majors, Degree=="Doctorate"), rownames=FALSE)
```

## Certificate

```{r, eval=TRUE}
	DT::datatable(subset(majors, Degree=="Certificate"), rownames=FALSE)
```

## Associates

```{r, eval=TRUE}
	DT::datatable(subset(majors, Degree=="Associates"), rownames=FALSE)
```
