---
output:
  html_document:
    self_contained: false
    includes:
      in_header: GA_Script.html
params:
  raw_table: "nothing"
  students_by_state_by_institution: "nothing"
  focal_state_long: "nothing"
  focal_state_abbr: "nothing"
title: "`r paste0('Where do students from ', params$focal_state_long, ' go?')`"


---

This shows where students from each state first go to college, based on the numbers reported by colleges that report student origins (most do this but not all). The count is the number of students in each college as freshmen (in Fall 2019, before covid hit); the percentage is this number divided by the number of 18 year old students of that state (then converted to a percentage). Not all freshmen are 18 years old (some could be 12, some could be 99), but this is a good way to get an estimate of what percentage of an age cohort goes to each school. For example, if it's 5%, that means that about 1 in 20 people graduating high school go to this college as freshmen. This only considers schools in the US, as well, given the data come from the US federal government.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(dev="png")
source("_packages.R")
source("R/functions.R")
tar_load(state_pops)
raw_table_df <- as.data.frame(params$raw_table)
raw_table_df$Institution <- raw_table_df$ShortName
students_by_state_list <- params$students_by_state_by_institution

students_to_institution <- data.frame(Institution=names(students_by_state_by_institution), StudentsFromFocalState=rep(0, length(students_by_state_by_institution)), InstitutionListsStateData = rep(FALSE,length(students_by_state_by_institution)))
for (institution_index in sequence(length(students_by_state_by_institution))) {
	students_to_institution[institution_index, 'StudentsFromFocalState'] <- as.numeric((students_by_state_by_institution[[institution_index]])[which(students_by_state_by_institution[[institution_index]]$State==params$focal_state_long),'Number of students'])
	students_to_institution[institution_index, 'InstitutionListsStateData'] <- ifelse(sum(as.numeric(students_by_state_by_institution[[institution_index]]$'Number of students'), na.rm=TRUE)==0, FALSE, TRUE)
}
students_to_institution <- students_to_institution[order(students_to_institution$Students, decreasing=TRUE),]

students_to_institution <- base::merge(students_to_institution, raw_table_df, by="Institution")
students_to_institution <- dplyr::select(students_to_institution, c(
	"Institution",
	"StudentsFromFocalState",
	"City",
	"State",
	"Type",
	"Undergraduate enrollment",
	"InstitutionListsStateData",
	"URL"
))

for (institution_index in sequence(nrow(students_to_institution))) {
	students_to_institution$Institution[institution_index] <- paste0("<a href='https://collegetables.info/", students_to_institution$URL[institution_index], "'>", students_to_institution$Institution[institution_index], "</a>")
}


students_to_institution <- dplyr::select(students_to_institution, -"URL")

institutions_with_no_data <- subset(students_to_institution, InstitutionListsStateData==FALSE)
institutions_with_no_data <- dplyr::select(institutions_with_no_data, -"InstitutionListsStateData")
students_to_institution <- dplyr::select(students_to_institution, -"InstitutionListsStateData")


institutions_with_no_data_focal_state <- subset(institutions_with_no_data, State==params$focal_state_abbr)

students_to_institution <- subset(students_to_institution, StudentsFromFocalState>0)

Total18YearOlds <- (subset(state_pops, State==params$focal_state_long))$Population_age_18

students_to_institution$'Percentage of state 18 y.o. going here' <- round(100*students_to_institution$StudentsFromFocalState/Total18YearOlds,4)
colnames(students_to_institution) <- gsub("StudentsFromFocalState", "Students from this state", colnames(students_to_institution))
students_to_institution <- students_to_institution[order(as.numeric(students_to_institution$"Students from this state"), decreasing=TRUE),]
rownames(students_to_institution) <- NULL

```

Most universities list how many students come from each state, but not all do. This page has two tables: a list of all institutions that report having students from this state ordered by the number of students from the focal state, and a table of all other institutions in that state, ordered by overall undergraduate enrollment. It is likely that in state institutions pull many of their students from their home state, but this is hard to assess without them reporting the data.

### Institutions with information on enrollment by state

```{r, echo=FALSE, message=FALSE, warning=FALSE}

students_to_institution %>% htmlTable::addHtmlTableStyle(col.rgroup = c("none", "#F7F7F7")) %>%  htmlTable::addHtmlTableStyle(pos.caption = "bottom") %>% htmlTable::htmlTable(escape.html=FALSE, rnames=FALSE)
```



### In state institutions without information on enrollment by state

```{r, echo=FALSE, message=FALSE, warning=FALSE}
rownames(institutions_with_no_data_focal_state) <- NULL
institutions_with_no_data_focal_state <- institutions_with_no_data_focal_state %>% dplyr::select(c("Institution", "City", "Type", "Undergraduate enrollment"))
institutions_with_no_data_focal_state <- institutions_with_no_data_focal_state[order(as.numeric(institutions_with_no_data_focal_state$'Undergraduate enrollment'), decreasing=TRUE),]
institutions_with_no_data_focal_state %>% htmlTable::addHtmlTableStyle(col.rgroup = c("none", "#F7F7F7")) %>%  htmlTable::addHtmlTableStyle(pos.caption = "bottom") %>% htmlTable::htmlTable(escape.html=FALSE, rnames=FALSE)
```