---
output: 
  html_document:
    includes:
      in_header: GA_Script.html
params:
  institution_name: "nothing"
  overview_table: "nothing"
  raw_table: "nothing"
title: "`r paste0(params$institution_name)`"

---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(dev="png")
focal_raw <- as.data.frame(params$raw_table)
focal_raw <- subset(focal_raw, focal_raw$"Institution Name"==params$institution_name)
```

### General information


* `r params$overview_table['Sector']`
* `r params$overview_table['Type']`
* It is `r paste0(ifelse(params$overview_table['Historically Black College or University']=="Yes","", "not "), "an historically black college or university (HBCU)")`
* Its undergraduate enrollment is `r format(as.numeric(params$overview_table["Undergraduate enrollment"]),big.mark=",", scientific=FALSE)`


### Diversity among the faculty

Two things to note here are diversity overall as well as the distribution tenure, tenure track, and non tenure track faculty. There are two main tracks in academia: faculty who are given short term contracts (and often a high teaching load and lower pay) and faculty who 

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=(nrow(focal_raw)==1)}
instructor_levels <- gsub("Black or African American men ", "", colnames(focal_raw)[grepl("Black or African American men \\(Full", colnames(focal_raw))])
instructor_groups <- unique(gsub(" \\(.*\\)", "", colnames(focal_raw)[grepl("Full-time instructional", colnames(focal_raw))]))

get_level <- function(x) {
	return(unname(gsub("\\)", "", strsplit(x, "  +")[[1]][2])))
}
professional_levels <- unique(sapply(instructor_levels, get_level))
professional_levels <- professional_levels[!is.na(professional_levels)]
combinations <- expand.grid(professional_levels = professional_levels, rank=c("(Full-time instructional not on tenure/no tenure system  ", "(Full-time instructional on-tenure track  ", "(Full-time instructional tenured  "))

faculty_counts <- matrix(0, nrow=length(instructor_groups), ncol=nrow(combinations))
rownames(faculty_counts) <- instructor_groups
colnames(faculty_counts) <- paste0(combinations$rank, combinations$professional_levels, ")")
for (row_index in sequence(nrow(faculty_counts))) {
	for(col_index in sequence(ncol(faculty_counts))) {
		try(faculty_counts[row_index, col_index] <- as.numeric(focal_raw[paste0(rownames(faculty_counts)[row_index], " ", colnames(faculty_counts)[col_index])]), silent=TRUE)
	}	
}
faculty_counts[which(is.na(faculty_counts))] <- 0
#faculty_counts <- faculty_counts[,which(colSums(faculty_counts)>0)]
colnames(faculty_counts) <- gsub('\\(Full-time instructional ', '', gsub('\\)', '', colnames(faculty_counts)))

faculty_counts_summary <- as.data.frame(matrix(0, nrow=nrow(faculty_counts), ncol=6))
rownames(faculty_counts_summary) <- rownames(faculty_counts)
colnames(faculty_counts_summary) <- c("Tenured (count)", "Tenure-track (count)", "Non-tenure-track (count)", "Tenured (percent)", "Tenure-track (percent)", "Non-tenure-track (percent)")
total_faculty <- sum(sum(faculty_counts[c("Grand total men", "Grand total women"),]))
faculty_counts_summary[,4:6] <- as.character(faculty_counts_summary[,4:6])
# tenured
matching_cols <- which(grepl("tenured", colnames(faculty_counts)))
for (row_index in sequence(nrow(faculty_counts_summary))) {
  if(length(matching_cols)>=1) {
  	faculty_counts_summary[row_index,1] <- sum(faculty_counts[row_index,matching_cols])
  	faculty_counts_summary[row_index,4] <- paste0(100*round(faculty_counts_summary[row_index,1]/total_faculty,3), "%")
  }
}
# tt
matching_cols <- which(grepl("on-tenure", colnames(faculty_counts)))
for (row_index in sequence(nrow(faculty_counts_summary))) {
  if(length(matching_cols)>=1) {
  	faculty_counts_summary[row_index,2] <- sum(faculty_counts[row_index,matching_cols])
  	faculty_counts_summary[row_index,5] <- paste0(100*round(faculty_counts_summary[row_index,2]/total_faculty,3), "%")
  }
}
# ntt
matching_cols <- which(grepl("no tenure", colnames(faculty_counts)))
for (row_index in sequence(nrow(faculty_counts_summary))) {
  if(length(matching_cols)>=1) {
  	faculty_counts_summary[row_index,3] <- sum(faculty_counts[row_index,matching_cols])
  	faculty_counts_summary[row_index,6] <- paste0(100*round(faculty_counts_summary[row_index,3]/total_faculty,3), "%")
  }
}

knitr::kable(faculty_counts_summary, row.names=TRUE)
```

### Diversity among the students

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=(nrow(focal_raw)==1)}
student_demographics <- gsub(" \\(EF2019A_RV  Full-time students  Undergraduate total\\)", "", colnames(focal_raw)[grepl("(EF2019A_RV  Full-time students  Undergraduate total)", colnames(focal_raw))])


student_types <- c("(EF2019A_RV  Full-time students  Undergraduate total)", "(EF2019A_RV  Full-time students  Graduate)")

combinations <- expand.grid(student_demographics = student_demographics, rank=student_types)


student_counts <- as.data.frame(matrix(0, nrow=length(student_demographics), ncol=length(student_types)))
rownames(student_counts) <- student_demographics
colnames(student_counts) <-student_types
for (row_index in sequence(nrow(student_counts))) {
	for(col_index in sequence(ncol(student_counts))) {
		try(student_counts[row_index, col_index] <- as.numeric(focal_raw[paste0(rownames(student_counts)[row_index], " ", colnames(student_counts)[col_index])]), silent=TRUE)
		if(is.na(student_counts[row_index, col_index])) {
			student_counts[row_index, col_index] <- 0	
		}
	}	
}

total_undergrads <- student_counts[1,1] + student_counts[2,1]
total_grads <- student_counts[1,2] + student_counts[2,2]
colnames(student_counts) <- c("Undergrad (count)", "Grad student (count)")
student_counts$`Undergrads (percent)` <- "0%"
student_counts$`Grad students (percent)` <- "0%"
for (i in sequence(nrow(student_counts))) {
	student_counts[i,3] <- paste0(round(100*student_counts[i,1]/total_undergrads,1), '%')
	student_counts[i,4] <- paste0(round(100*student_counts[i,2]/total_grads,1), '%')

}

knitr::kable(student_counts, row.names=TRUE)
```

### US student origins

First time degree seeking undergrads

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=(nrow(focal_raw)==1)}
Students_by_state <- data.frame(fips=rep(NA,  length(state.name)), abbr=state.abb, Name=state.name, Undergrad_Count=rep(0.0, length(state.name)), Percent_of_18_yo_from_this_state_enrolled_here=rep(0.0, length(state.name)))

state_pops <- GetPopulationByStateAtAge18()

for (i in sequence(nrow(Students_by_state))) {
	Students_by_state$Undergrad_Count[i] <- unname(unlist(focal_raw[paste0("Count of first-time undergrads from ", Students_by_state$Name[i])]))
	Students_by_state$Percent_of_18_yo_from_this_state_enrolled_here[i] <- unname(unlist(focal_raw[paste0("Percentage of all 18 year olds in the focal state enrolling in this college from ", Students_by_state$Name[i])]))
	if(is.na(Students_by_state$Undergrad_Count[i])) {
		Students_by_state$Undergrad_Count[i] <- 0
		Students_by_state$Percent_of_18_yo_from_this_state_enrolled_here[i] <- 0
	}
	Students_by_state$fips[i] <- state_pops$State_FIPS[which(state_pops$State==Students_by_state$Name[i])]
}
count_data <- as.data.frame(select(Students_by_state, c("fips", "Undergrad_Count")))
colnames(count_data) <- c("fips", "values")
count_data$fips <- as.character(count_data$fips)
count_data$values[is.na(count_data$values)] <- 0
count_data[,2] <- as.numeric(count_data[,2])

plot_usmap(data=count_data, regions = "states", color = "blue") + labs(title=paste0("Number of students from each state enrolled in ",params$institution_name)) +
  scale_fill_continuous(low = "white", high = "blue", name = "Number of undergrads", label = scales::comma) +  theme(legend.position = "right")


pct_data <- select(Students_by_state, c("fips", "Percent_of_18_yo_from_this_state_enrolled_here"))
colnames(pct_data) <- c("fips", "values")
pct_data$fips <- as.character(pct_data$fips)
pct_data$values <- as.numeric(pct_data$values)

plot_usmap(data=pct_data, regions = "states", color = "blue") + labs(title=paste0("Percentage of 18 year olds in each state enrolled in ",params$institution_name)) +
  scale_fill_continuous(low = "white", high = "blue", name = "Percentage (out of 100)", label = scales::comma) +  theme(legend.position = "right")

```

